### 2024-05-16 fantasy-football.qmd
20240516 - typo

As noted in the [Introduction](intro.qmd) Fantasy football is an online game where participants assemble (i.e., "draft") imaginary teams composed of real-life National Football League (NFL) players.
A fantasy football "league" is composed of various participants (each of whom has an imaginary team), and they play against each other.
Leagues are commonly composed of 8 or 10 teams, but leagues can have more or fewer participants/teams.
In the game of fantasy football, participants accumulate points on a weekly basis based on players' actual statistical performances in NFL games.
A participant's goal is to outscore their opponent each week to win matches and ultimately claim victory in the league.

>>>>

As noted in the [Introduction](intro.qmd), fantasy football is an online game where participants assemble (i.e., "draft") imaginary teams composed of real-life National Football League (NFL) players.
A fantasy football "league" is composed of various participants (each of whom has an imaginary team), and they play against each other.
Leagues are commonly composed of 8 or 10 teams, but leagues can have more or fewer participants/teams.
In the game of fantasy football, participants accumulate points on a weekly basis based on players' actual statistical performances in NFL games.
A participant's goal is to outscore their opponent each week to win matches and ultimately claim victory in the league.
